---
title: "Contiguous US Maps"
author: "Martin John Hadley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(statesRcontiguous)
```

# Visualising the contiguous United States

This package provides three different shapefiles for the United States of America, comprising; state boundaries, congressional districts and counties. These are stored as `sf` objects, if you're not familiar with the excellent `sf` approach to geometric features it's highly recommended you glace at the documentation - https://r-spatial.github.io/sf//index.html

The `sf` objects contain a column called `contiguous.united.states` which allows us to restrict ourselves to only the contiguous US. This is how we might visualise the congressional districts of the contiguous US with leaflet:

```{r}
library("statesRcontiguous")
library("leaflet")
shp_contiguous_us_congressional_districts <- shp_all_us_congressional_districts %>%
  filter(contiguous.united.states)
shp_contiguous_us_congressional_districts %>%
  leaflet() %>%
  addTiles() %>%
  addPolygons(weight = 1)
```

# Where are the shapefiles from?

All of the shapefiles in this package are from the US Census website - https://www.census.gov/geo/maps-data/data/tiger-cart-boundary.html. This package will continuously be updated with the most recent shapefiles, historical shapefiles will **not** be available in this package. If that's what you want, please do use the `tigris` package - https://github.com/walkerke/tigris.

The explicit urls for the shapefiles are available here:

```{r}
knitr::kable(shapefile_details)
```


